Are we living in a depressive society?

### 2024-04-03 outputs/paper/paper.qmd
commit

>>>>

# Load necessary libraries
library(tidyverse)
library(lubridate)

# Define the path to the data file and load it
data <- read.csv(file = here::here("outputs/data/Overall_trends.csv"))

# Filter the dataset for the specified symptoms
filtered_data <- data %>%
  filter(Indicator %in% c('Symptoms of Depressive Disorder', 
                          'Symptoms of Anxiety Disorder', 
                          'Symptoms of Anxiety Disorder or Depressive Disorder'))

# Define the sequence of dates for x-axis breaks, starting from the first date, incrementing by 4 months
start_date <- as.Date("2020-05-05")
end_date <- as.Date("2024-03-04")

# Manually define the specific dates you want to mark on the x-axis
specific_dates <- as.Date(c("2020-05-05", "2020-09-14", "2021-01-05", 
                            "2021-05-10", "2021-09-13", "2022-01-10", 
                            "2022-05-09", "2022-09-13", "2023-01-16",
                            "2023-05-08", "2023-09-04", "2024-01-08"))

# Plotting the line graph
ggplot(filtered_data, aes(x = Time.Period.End.Date, y = Value, group = Indicator, color = Indicator)) +
  geom_line() +
  labs(title = "Overall Symptom Rates Trend",
       x = "Date",
       y = "Symptom Rates (%)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        plot.margin = unit(c(1, 1, 1, 1), "cm"))
